RDF Constraints Classification Ensuring \\ High Quality of Metadata and Data

### 2015-04-20 paper/paper7/paper7.tex
technology-driven constraint types

\textbf{Disjointness and Allowed Values.}
All properties, not having the same domain and range classes, are defined to be pairwise disjoint
(\emph{R-9: disjoint properties}), stating that no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties like \emph{phdd:isStructuredBy} and \emph{phdd:column} ($isStructuredBy \sqsubseteq \neg column$).
All \emph{XKOS} classes are pairwise disjoint (\emph{R-7: disjoint classes}; e.g. \ms{ClassificationLevel $\sqcap$ ConceptAssociation $\sqsubseteq$ $\perp$}),
i.e., individuals cannot be instances of multiple disjoint classes.
It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values.  
\emph{Allowed values} (\emph{R-30, R-37}) for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g. 'red' 'blue' 'green'), and typed literals of one or multiple type(s) (e.g. \emph{xsd:string}) - 
\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString} (\ms{CategoryStatistics $\equiv$ $\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}).

\textbf{Validation and Reasoning.}
Some constraint types enable performing reasoning prior to validation which may resolve or cause constraint violations.
With \emph{subsumption} (\emph{R-100}) one can state that \emph{xkos:ClassificationLevel} is a sub-class of \emph{skos:Collection}, i.e., each \emph{xkos:ClassificationLevel} resource must also be part of the \emph{skos:Collection} class extension (\ms{ClassificationLevel $\sqsubseteq$ Collection}).
With \emph{sub properties} (\emph{R-54, R-64}) one can state that \emph{disco:fundedBy} is a sub-property of \emph{dcterms:contributor} - i.e., if a study is funded by an organization, then this organization contributed to this study (\ms{fundedBy $\sqsubseteq$ contributor}).
\emph{Asymmetric object properties} (\emph{R-62}) restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}. 
Such constraints are defined for each object property for which a semantically equivalent object property pointing from the other direction would also be possible but is not defined within the vocabulary.
A \emph{disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a \emph{disco:RepresentedVariable}.
A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$disco:basedOn \sqcap disco:basedOn^{-} \sqsubseteq \bot$}).
\emph{Default values} (\emph{R-31, R-38}) for objects/literals of given prooperties are inferred automatically when properties are not present.
The value \emph{true} for the property {\em disco:isPublic} indicates that a {\em disco:LogicalDataSet} can be accessed by anyone.
Per default, however, access to data sets should be restricted (\emph{false}).
Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
If \emph{dcterms:coverage} and one of its sub-properties (\emph{dcterms:spatial}, \emph{dcterms:temporal}) are present,
it is checked that \emph{dcterms:coverage} is not redundant with its sub-properties. 
This validation can indicate when the data is verbose (redundant) or expressed at a too general level and could thus be improved.

@@

For \emph{Disco} and \emph{SKOS}, more than the half of the constraints are associated with the weakest severity level $\mathcal{SL}_{0}$.
Within the context of \emph{QB}, 80\% of the constraints are classified as the most serious ones ($\mathcal{SL}_{2}$).
All in all, there are a little bit more $\mathcal{SL}_{0}$ then $\mathcal{SL}_{2}$ constraints, whereas $\mathcal{SL}_{1}$ constraints are negligible.
\emph{Existential quantifications} (32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
By validating \emph{QB} data sets, we got the most constraint violations (more than 45 millions), followed by \emph{SKOS} and \emph{Disco} (with more than 5.5 and 3.5 millions) - consequently, almost 55 million constraint violations were raised during the evaluation which could be used to enhance the metadata quality of these data sets.  
Close to 70\% of all \emph{Disco} constraint violations are caused by violating $\mathcal{SL}_{0}$ constraints.
For \emph{QB} (nearly 100\%) and \emph{SKOS} (almost 60\%), the majority of the raised constraint violations are classified to be more serious ($\mathcal{SL}_{1}$).
80\% of all \emph{QB} constraints are $\mathcal{SL}_{2}$ constraints leading to less than 1\% of all \emph{QB} constraint violations.
Altogether, exactly 90\% of the constraint violations are assigned to the severity level $\mathcal{SL}_{1}$.
These findings are surprising as only 8\% of all defined constraints are $\mathcal{SL}_{1}$ constraints.
The constraints responsible for the largest numbers of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916) (\emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102) (\emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903) (\emph{SKOS})\tb{kurz beschreiben}.
We refer to the technical reports\footnotemark[\ref{technical-report-1}] \footnotemark[\ref{technical-report-2}] to get details about constraints on and the evaluation of \emph{XKOS} and \emph{PHDD} data sets.

>>>>

\textbf{Disjointness and Allowed Values.}
All properties, not having the same domain and range types, are defined to be pairwise disjoint
(\emph{R-9: disjoint properties}), i.e., no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties like \emph{phdd:isStructuredBy} and \emph{phdd:column} ($isStructuredBy \sqsubseteq \neg column$).
All \emph{XKOS} classes are pairwise disjoint (\emph{R-7: disjoint classes}; e.g. \ms{ClassificationLevel $\sqcap$ ConceptAssociation $\sqsubseteq$ $\perp$}),
i.e., individuals cannot be instances of multiple disjoint classes.
It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values.  
\emph{Allowed values} (\emph{R-30, R-37}) for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g. 'red' 'blue' 'green'), and typed literals of one or multiple type(s) (e.g. \emph{xsd:string}). 
\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString} (\ms{CategoryStatistics $\equiv$ $\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}).

\textbf{Validation and Reasoning.}
Some constraint types enable performing reasoning prior to validation which may resolve or cause constraint violations.
With \emph{subsumption} (\emph{R-100}), one can state that \emph{xkos:ClassificationLevel} is a sub-class of \emph{skos:Collection}, i.e., each \emph{xkos:ClassificationLevel} must also be part of the \emph{skos:Collection} class extension (\ms{ClassificationLevel $\sqsubseteq$ Collection}).
With \emph{sub properties} (\emph{R-54, R-64}), one can state that \emph{disco:fundedBy} is a sub-property of \emph{dcterms:contributor} - i.e., if a study is funded by an organization, then this organization contributed to this study (\ms{fundedBy $\sqsubseteq$ contributor}).
%\emph{Asymmetric object properties} (\emph{R-62}) restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}. 
%Such constraints are defined for each object property for which a semantically equivalent object property pointing from the other direction would also be possible but is not defined within the vocabulary.
%A \emph{disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a \emph{disco:RepresentedVariable}.
%A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$disco:basedOn \sqcap disco:basedOn^{-} \sqsubseteq \bot$}).
\emph{Default values} (\emph{R-31, R-38}) for objects/literals of given properties are inferred automatically when properties are not present in the data.
The value \emph{true} for the property {\em disco:isPublic} indicates that a {\em disco:LogicalDataSet} can be accessed by anyone.
Per default, however, access to data sets should be restricted (\emph{false}).
Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
If \emph{dcterms:coverage} and one of its sub-properties (\emph{dcterms:spatial}, \emph{dcterms:temporal}) are present,
it is checked that \emph{dcterms:coverage} is not redundant with its sub-properties. 
This validation can indicate when the data is verbose (redundant) or expressed at a too general level and could thus be improved.

@@

For \emph{Disco} and \emph{SKOS}, more than the half of the constraints are associated with the weakest severity level $\mathcal{SL}_{0}$.
Within the context of \emph{QB}, 80\% of the constraints are classified as the most serious ones ($\mathcal{SL}_{2}$).
All in all, there are a little bit more $\mathcal{SL}_{0}$ then $\mathcal{SL}_{2}$ constraints, whereas $\mathcal{SL}_{1}$ constraints are negligible.
\emph{Existential quantifications} (32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
By validating \emph{QB} data sets, we got the most constraint violations (more than 45 millions), followed by \emph{SKOS} and \emph{Disco} (with more than 5.5 and 3.5 millions) - consequently, almost 55 million constraint violations were raised during the evaluation which could be used to enhance the metadata quality of these data sets.  
Close to 70\% of all \emph{Disco} constraint violations are caused by violating $\mathcal{SL}_{0}$ constraints.
For \emph{QB} (nearly 100\%) and \emph{SKOS} (almost 60\%), the majority of the raised constraint violations are classified to be more serious ($\mathcal{SL}_{1}$).
80\% of all \emph{QB} constraints are $\mathcal{SL}_{2}$ constraints leading to less than 1\% of all \emph{QB} constraint violations.
Altogether, exactly 90\% of the constraint violations are assigned to the severity level $\mathcal{SL}_{1}$.
These findings are surprising as only 8\% of all defined constraints are $\mathcal{SL}_{1}$ constraints.
The constraints responsible for the largest numbers of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916) (\emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102) (\emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903) (\emph{SKOS}).
We refer to the technical reports\footnotemark[\ref{technical-report-1}] \footnotemark[\ref{technical-report-2}] to get details about constraints on and the evaluation of \emph{XKOS} and \emph{PHDD} data sets.
